04_DESeq_sexes

### 2019-05-30 analysis/04_DESeq2_sexes.Rmd
now with group ave heatmaps

>>>>

## new heat maps

```{r correlationheatmaps, eval = T}

plotcorrelationheatmaps <- function(mydds, mycoldata, mysubtitle){
  dds <- mydds
  vsd <- vst(dds, blind=FALSE) # variance stabilized

  colnames(vsd) = mycoldata$treatment # set col names to group name

  vsdm <- assay(vsd) # create matrix

  vsdmmean <-sapply(unique(colnames(vsdm)), function(i)
  rowMeans(vsdm[,colnames(vsdm) == i]))

  myannotations <- mycoldata %>% 
    dplyr::distinct(lastday, penultimate, treatment) 
  rownames(myannotations) <- myannotations$treatment
  myannotations$treatment <- NULL

  mycor <- cor(vsdmmean)
  str(mycor)

  paletteLength <- 10
  myBreaks = c(0.91,0.92,0.93,0.94,0.95, 0.96, 0.97,0.98, 0.99, 1.0)

  myBreaks <-seq(0.95, 1.0, length.out = 10)
  myBreaks

  pheatmap(cor(vsdmmean),
          annotation_row = myannotations,
          annotation_col = myannotations,
          annotation_colors = myannotationscolors,
          annotation_names_row = F,
          main= mysubtitle,
          color = inferno(10),
          show_rowname= F, show_colnames = F,
          breaks = myBreaks
          )
}

colData.female_hypothalamus <- subsetcolData(a.colData,  "female_hypothalamus")
colData.female_pituitary <- subsetcolData(a.colData,  "female_pituitary" )
colData.female_gonad <- subsetcolData(a.colData,  "female_gonad" )
colData.male_hypothalamus <- subsetcolData(a.colData,  "male_hypothalamus" )
colData.male_pituitary <- subsetcolData(a.colData,  "male_pituitary"  )
colData.male_gondad <- subsetcolData(a.colData,  "male_gonad")

plotcorrelationheatmaps(dds.female_hypothalamus, colData.female_hypothalamus ,"female hypothalamus: hatch, nest building, lay and day-before-hatch cluster")
plotcorrelationheatmaps(dds.female_pituitary, colData.female_pituitary, "female pituitary: clustering suggests an internal clock effect")
plotcorrelationheatmaps(dds.female_gonad, colData.female_gonad,  "female gonad: highly correlated across incubation and early nestling care")
plotcorrelationheatmaps(dds.male_hypothalamus, colData.male_hypothalamus, "male hypothalamus: 100% correlated across most parental care stages")
plotcorrelationheatmaps(dds.male_pituitary, colData.male_pituitary, "male pituitary: non-parental males are most different")
plotcorrelationheatmaps(dds.male_gondad, colData.male_gondad, "male gonad: non-parental males are most different")
```
